---
title: "netCDF"
author: "Ben Williams"
date: "December 15, 2015"
output: html_document
---

Brief example of working with a netCDF file  
```{r}
library(ncdf)
library(ggplot2)
theme_set(theme_bw(base_size=18)+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
library(reshape2)
```

Import file  
```{r}
modis <- open.ncdf("MODIS_Chl_monthly.nc")
print(modis)
```

Pull out the variables  
```{r}
get.var.ncdf(modis,varid='longitude')->lon
get.var.ncdf(modis,varid='latitude')->lat
```

Adjust longitude to something I can use  
```{r}
lon<- lon -360
``` 

Set the Unix time to something understandable
```{r}
as.Date(as.POSIXct(modis$dim$time$vals, origin="1970-01-01")) -> time
```

Create a data.frame - (if your file has multiple variables this will pull all of them out):  
```{r}
out = expand.grid(latitude=lat,longitude=lon)

vars = names(modis$var) #get a list of the data in the netcdf file
for (voi in vars) { cat(voi,'...\n') #cycle through each of the variables
     tdata = get.var.ncdf(modis,voi) #read in the data array for the variable of interses
     for(ii in 1:length(time)) { out[,paste(time[ii])]  = as.vector(tdata[,,ii]) } #append the data to out
}
```

Melt the dataframe 
outer <- melt(out, id=c('longitude','latitude'))

Ditch the NAs to make a smaller file
```{r}
outer<-na.omit(outer)
```

Now subset etc. as you see fit.
